IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
last paragraph of node

\Red{LOCK:deian}
While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, our libraries provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This task is trusted to ensures that, for instance, labels are
propagated to files and that tasks are tainted when reading sensitive
files, as to preserve non-interference.
%
\Red{go into how this is app specific and it's not a huge limitation
  that our system does not capture this; e.g., even for fs semantics
  can vary: are labels serialized or not. later let's us change policy
more easily, the other is better for persistence}

>>>>

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
We, instead, implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, our libraries provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
(This is safer than the approach of simply wrapping objects, which can
potentially allow for accessing objects outside the context.)
%
This task is trusted to ensures that, for instance, labels are
propagated to files and the labels of the task performing the
operations and the file in question are inspected appropriately, as to
preserve non-interference.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this is also somewhat expected:
different language environments expose different libraries for
handling external I/O.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
different from our implementation, Hails~\cite{hails} does not persist
labels).
%
While we can extend our formalism to model a particular interface to
the file system, HTTP client, etc. the applicability of this are
unclear and left to future work.
%
